%----------------------------------------------------------------------------------------
%   INTERNSHIPS
%----------------------------------------------------------------------------------------

\subsection{Early Career Experience}
\begin{itemize}
    \item \footnotesize{TAPPS Games - Full Stack Software engineer intern, Mobile Casual Games 
        Development Team (05/2015-09/2015)}
    \begin{itemize}
        \item \scriptsize{Developed both new games and re-skins of old games as a backend and frontend
        developer for high-performance gaming applications.}
        \item \scriptsize{Contributed to the successful launch of 5 mobile games achieving over 30M
        downloads with average rating of 4.6+. Developed both backend and frontend components for
        gaming applications. Acted in the
        \href{https://www.youtube.com/watch?v=ttjWkk9w-8Q}{teaser video} of one of the games.}
    \end{itemize}
    
    \item \footnotesize{Google - Software Engineer Intern, Social Infrastructure team (12/2014-02/2015)}
    \begin{itemize}
        \item \scriptsize{Contributed to a system analyzing server profiles to detect performance 
            differences using hypothesis testing, which became a standard validation tool for the Social 
            org's production releases. It assessed whether systems updates, like Google+, outperformed
            previous versions and used veto power to prevent poorly performing updates from being 
            released, becoming part of a CI/CD pipeline.}
        \item \scriptsize{Improved the precision of statistical analysis by 10\% through enhancements to 
            the hypothesis testing methodology.}
    \end{itemize}

    \item \footnotesize{Drivedata Software - Full-Stack Software developer intern (10/2013-10/2014)}
    \begin{itemize}
        \item \scriptsize{0/1 Experience}
        \item \scriptsize{Designed and developed a Java Web application and an Android App related to vehicle insurance companies.}
        \item \scriptsize{Developed the signed in user interface web application and the android application that were shipped for the first launch of the company. Delivered production-ready code that was essential to the company's market entry.}
    \end{itemize}

    \item \normalsize{Full Stack Software developer intern at \textbf{CCSL}, Mezuro \& Kalibro Team}\\
        \scriptsize{São Paulo-SP, Brazil (Sep 2010-Jan 2013)}
    \begin{itemize}
        \item \footnotesize{Languages:}\scriptsize{ \textbf{Java}, \textbf{Ruby}, HTML, CSS, JavaScript}
        \item \footnotesize{Key Responsibilities:}\scriptsize{ Collaborated on the development of the Kalibro and Mezuro projects at CCSL (\href{http://ccsl.ime.usp.br/en}{ccsl.ime.usp.br/en}). Contributed to research on code metrics in Free/Libre and Open Source Software (FLOSS).}
        \item \footnotesize{Key Achievements:}\scriptsize{ Co-Presented and contributed to a Poster and a presentation with research and development results in international conferences, enhancing the academic community's understanding of code metrics. Contributed to the development of the Kalibro and Mezuro projects at CCSL, focusing on the advancement of tools for code metrics analysis.}
        \item \footnotesize{Note about this experience:}\scriptsize{ Since it was close to an academic environment we could follow XP programming and other agile practices by the book, such as TDD, Planning Game, on-site customer, Daily stand-ups, Kanban, Pair Programming and Continuous integration.}
    \end{itemize}
\end{itemize}