%-------------------------------------------------------------------------------------------------------
%   MICROSOFT
%-------------------------------------------------------------------------------------------------------

\normalsize{Microsoft - Software Engineer 2, Microsoft AI Spartans team}\\
    \scriptsize{São Paulo-SP, Brazil \& Redmond, WA, USA (06/2019 - 03/2025)}
\begin{itemize}
    \item \scriptsize{As part of Spartans, an elite engineering team, accelerated high-priority
        time-sensitive projects across Microsoft AI org by delivering target engineering solutions, and
        guiding teams through technical challenges to achieve measurable business outcomes. Demonstrated
        versatility in rapidly adopting new technologies based on project requirements.}

    \item \scriptsize{Worked with distributed storage solutions (Azure Data Lake, Azure Key-Value Data
        Store and HDFS) to handle multi-petabyte data volumes with proper consistency controls,
        implementing tiered storage strategies, sharding, replication and sophisticated error handling
        mechanisms for greater fault tolerance and data governance.}

%-------------------------------------------------------------------------------------------------------
%   PROJECTS
%   TODO: Divide those by project and remove redundant items
%-------------------------------------------------------------------------------------------------------
    \item \scriptsize{Led technology migration of Bing's Content Discovery \& Selection critical offline
        pipelines from Cosmos Scope to Apache Spark, reducing operational costs by 20\% across
        large-scale data platform services while optimizing performance for processing petabytes of data 
        in enterprise-scale while maintaining business continuity, resulting in potential savings
        in the hundreds of millions of dollars.}

    \item \scriptsize{Enhanced data freshness for Food Recipes pipeline from 7 days to under 2 days by
        optimizing pipeline performance and transitioning from weekly to daily execution, making it the
        first project to adopt a new document ingestion platform.}

    \item \scriptsize{Reengineered Pipeline management framework, resulting in 30\% performance
        improvement across all Bing's Content Discovery \& Selection bucketed pipelines without
        requiring modification to job implementations.}

    \item \scriptsize{Architected complex goroutine parallelization with custom pooling and queueing
        systems for retry caching in Microsoft Ads logging infrastructure, orchestrating Go and Java
        components via Kubernetes while integrating with Azure Service Bus, measurably improving data
        throughput, consistency and reliability.}
    
    \item \scriptsize{Designed and implemented highly scalable backend services, including
        microservice architectures for low-latency critical services and RESTful APIs, like the Bing's Image Creator's UserHistoryV2 REST API, focusing on scalability, maintainability, security, and service isolation that suppported millions of daily requests. Managed to reduce API calls to other services by 90\% compared to previous implementation by deploying refined caching strategies.}
    
    \item \scriptsize{Established monitoring systems with alerting capabilities to maintain 99.9\%
        service availability with rapid incident response across many projects.}

    \item \scriptsize{Designed BI dashboards that transformed raw data into visual analytics, enabling
        data-informed strategy development and quantifiable business outcomes.}

    \item \scriptsize{Integrated Sponsored Stories in Microsoft Ads, generating \$2.5M in revenue for
        high-traﬀic integrations while ensuring seamless user experience.}

    \item \scriptsize{Leveraged Knowledge Cards template system with flexible schema design, expanding
        data scalability and enabling the addition of over 100 million entities while maintaining
        sub-100ms response times.}

    \item \scriptsize{Crafted financial tracking and inventory management systems for Microsoft Rewards
        integration, implementing secure transaction processing with robust audit trails.}

    \item \scriptsize{Built comprehensive test automation and CI/CD pipelines to ensure high code 
        quality, reliability, faster bug detections and faster releases.}

    \item \scriptsize{Developed specialized testing tools including a Diff job tool for validating 
        migrated pipeline outputs and implemented Nightwatch tests for API endpoints, improving system
        reliability.}

    \item \scriptsize{Architected multilingual Query Parser pipelines changes to support 40+ languages 
        and markets, implementing sophisticated parallel processing techniques that maintained high 
        accuracy while enabling seamless multilingual integration.}
    
    \item \scriptsize{Applied advanced performance optimization techniques to critical data pipelines, 
        reducing execution time from 10-20 hours to approximately 5 hours through improved 
        parallelization strategies and resource allocation.}
    
    \item \scriptsize{Reengineered PipelineManager configuration framework, resulting in 30\% 
        performance increase across all bucketed pipelines in the Discovery org without requiring 
        modification to job implementations.}
        
    \item \scriptsize{Designed and implemented innovative catchup solution for historical data 
        processing, reducing estimated catchup time from 6 months to 1 week for a business-critical data 
        pipeline through intelligent data partitioning and incremental processing.}
        
    \item \scriptsize{Successfully managed complex pipeline migrations with zero downtime, maintaining 
        system stability during transitions through comprehensive planning, testing, and rollback 
        strategies.}

    \item \scriptsize{Designed and implemented microservice architectures for critical systems including 
        the ImageGenerator UserHistory API and MMSBI logging system, focusing on scalability, 
        maintainability, and service isolation to support user token management and integration with 
        external systems.}
        
    \item \scriptsize{Applied advanced distribution patterns including sharding when processing logs and 
        implemented sophisticated caching strategies that reduced the number of API calls to Rewards and 
        third-party systems by 90\% while significantly reducing latency for high-volume operations.}
        
    \item \scriptsize{Architected Knowledge Cards template system using a flexible schema design, 
        increasing data scalability and enabling the addition of over 100 million entities while 
        maintaining sub-100ms response times.}
        
    \item \scriptsize{Led integration with multiple external payment and authentication systems (e.g., 
        PayPal, Rewards), implementing secure token exchange protocols to ensure reliable and secure 
        data transactions between disparate platforms.}
        
    \item \scriptsize{Developed a generic Refund API and comprehensive Points Inventory Management 
        System for Microsoft Rewards with a future-proof architecture designed to accommodate evolving 
        business requirements beyond initial specifications.}
        
    \item \scriptsize{Engineered sophisticated goroutine parallelization with custom pooling and 
        queueing systems for retry caching in the Microsoft Ads logging infrastructure, significantly 
        improving throughput while maintaining data consistency.}
        
    \item \scriptsize{Leveraged replication patterns in Microsoft Cosmos and HDFS to ensure data 
        durability and processing efficiency across distributed systems.}
        
    \item \scriptsize{Enhanced auto-replenish feature for ImageGenerator tokens through sophisticated 
        business logic that balanced conflicting requirements from multiple stakeholders while 
        maintaining a seamless user experience.}
    
    \item \scriptsize{Developed tools and libraries, which streamlined migration validation, ensuring 
        accurate and efficient workflows.}
        
    \item \scriptsize{Leveraged CI/CD pipelines to streamline deployment processes, enabling faster 
        release cycles and reducing production incidents.}
        
    \item \scriptsize{Enhanced internal tools with new safety measures, logging, and configuration 
        options, boosting reliability and scalability.}
        
    \item \scriptsize{Designed and delivered comprehensive analytics dashboards integrating 
        visualization technologies.}
        
    \item \scriptsize{Created testing tools including a Diff job tool for validating migrated pipeline 
        outputs and Nightwatch tests for API endpoints.}
        
    \item \scriptsize{Updated security on internal spark modules to passwordless AAD Token 
        authentication, enhancing system security while maintaining ease of use.}
        
    \item \scriptsize{Became second top committer to core WebDataPlatform team's PipelineManager through 
        numerous improvements and features.}
        
    \item \scriptsize{Improved repository infrastructure through Corext aliases enhancements, boosting 
        development efficiency.}

    \item \scriptsize{Implemented logging infrastructure improvements for Microsoft Ads, preventing data 
        loss and increasing reliability for BI decisions.}
        
    \item \scriptsize{Integrated Sponsored Stories in Microsoft Ads, generating ~\$2.5M in revenue for 
        high-traffic integrations.}
        
    \item \scriptsize{Supported UX enhancements for Knowledge Cards, improving accessibility and 
        creating visually appealing templates for diverse content types.}
        
    \item \scriptsize{Successfully enabled product deployment in international markets, expanding global 
        reach for services including Trending Topics for Microsoft Ads and Bing Search's QueryParser.}
        
    \item \scriptsize{Identified and resolved critical bugs affecting end users, including a 
        long-standing high-priority issue related to non-trending content in trending scenarios.}
        
    \item \scriptsize{Facilitated comprehensive knowledge transfer and onboarding sessions for team 
        members on both internal tools like Cosmos and public tools like .NET Spark.}
        
    \item \scriptsize{Successfully completed handoff of complex systems with detailed documentation, 
        ensuring seamless transitions.}

    \item \scriptsize{Led incident response teams diagnosing and resolving complex production issues 
        under high-pressure situations across distributed systems.}
        
    \item \scriptsize{Built automated recovery systems that could detect, diagnose, and remediate 
        service failures with minimal interruption.}
        
    \item \scriptsize{Created systematic approaches to identify potential system vulnerabilities through 
        proactive monitoring and analysis.}
        
    \item \scriptsize{Implemented comprehensive monitoring and alerting systems that significantly 
        reduced mean time to detection for production incidents, improving overall system reliability.}

    \item \scriptsize{Led incident response teams diagnosing and resolving complex production issues 
        under high-pressure situations across distributed systems.}
        
    \item \scriptsize{Built automated recovery systems that could detect, diagnose, and remediate 
        service failures with minimal interruption.}
        
    \item \scriptsize{Applied advanced distribution patterns including sharding when processing logs and 
        implemented sophisticated caching strategies that reduced API calls by 90\% while significantly 
        reducing latency.}
        
    \item \scriptsize{Engineered sophisticated goroutine parallelization with custom pooling and 
        queueing systems, significantly improving throughput while maintaining data consistency.}
        
    \item \scriptsize{Leveraged replication patterns in Microsoft Cosmos and HDFS to ensure data 
        durability and processing efficiency across distributed systems.}

    \item \scriptsize{Actively participated in neurodiversity and mental health initiatives that
        improved team collaboration and support for neurodivergent individuals by mentoring colleagues,
        advocating for inclusive workplace practices and being a founding member of the Mental Health \&
        Neurodiversity group within the local Disability ERG chapter in Brazil.}
\end{itemize}