%----------------------------------------------------------------------------------------
%	PROFESSIONAL DEVELOPMENT
%----------------------------------------------------------------------------------------

\section{Professional Development}
\begin{itemize}
    \item \footnotesize{Microsoft Professional Development (01/2019-03/2025):}
    \begin{itemize}
        \item \scriptsize{Responsible AI Learning Path (4-hour), focusing on ethical AI implementation, governance and bias mitigation.}
        \item \scriptsize{Copilot Prompt Engineering Learning Path (8-hour) training path covering advanced LLM interaction techniques.}
        \item \scriptsize{Leadership Principles Learning Path (4-hour).}
        \item \scriptsize{Advanced Cloud Architectures Learning Path (4-hour).}
    \end{itemize}
    \item \footnotesize{K19 Trainings (01/2011-12/2011):}\scriptsize{ Completed specialized training in Web Development with JSF2 and JPA, Persistence with JPA2 and Hibernate, Advanced Web Development, and System Integration with Web services.}
    \item \footnotesize{Caelum Trainings (01/2009-12/2009):}\scriptsize{ Foundational training in Java and OO, Java Laboratory with Tests, XML and Design Patterns, and Java for WEB Development.}
    \item \footnotesize{Conferences:}
    \begin{itemize}
        \item \scriptsize{International Conference on ADHD (2020-2022): Attended three consecutive 
            annual conferences focusing on neurodiversity, workplace inclusion, and mental health
            awareness.}
        \item \scriptsize{International Conference on Open Source Systems (10/2011): Presented research
            on multi-repository code metrics analysis tools.}
        \item \scriptsize{FISL13 (07/2012): Presented on open-source code monitoring networks.}
    \end{itemize}
\end{itemize}