%----------------------------------------------------------------------------------------
%   MICROSOFT
%----------------------------------------------------------------------------------------

\normalsize{Microsoft - Software Engineer 2, Microsoft AI Spartans team}\\
        \scriptsize{São Paulo-SP, Brazil \& Redmond, WA, USA (06/2019 - 03/2025)}
\begin{itemize}
    \item \scriptsize{As part of Spartans, an elite engineering team, accelerated high-priority time-sensitive
        projects across Microsoft AI org by delivering targeted engineering solutions, and guiding teams through
        technical challenges to achieve measurable business outcomes. Demonstrated versatility in rapidly adopting
        new technologies based on project requirements.}

    \item \scriptsize{Established monitoring systems with alerting capabilities to maintain 99.9\% service
        availability with rapid incident response, ensuring business-critical services remained accessible to
        millions of users.}

    \item \scriptsize{Designed and implemented microservice architectures for Low-Latency critical services,
        including Bing's Image Creator UserHistoryV2 REST API, focusing on scalability, maintainability, and
        service isolation.}

    \item \scriptsize{Crafted financial tracking and inventory management systems for Microsoft Rewards
        integration, implementing secure transaction processing with robust audit trails to support millions of users.}

    \item \scriptsize{Worked with distributed storage solutions (Azure Data Lake, Azure Key-Value Data Store and
        HDFS) to handle multi-petabyte data volumes with proper consistency controls, implementing tiered storage
        strategies and sophisticated error handling mechanisms for greater fault tolerance and data governance.}

    \item \scriptsize{Architected complex goroutine parallelization with custom pooling and queueing systems
        for retry caching in Microsoft Ads logging infrastructure, orchestrating Go and Java components via
        Kubernetes while integrating with Azure Service Bus, measurably improving data throughput, consistency
        and reliability.}

    \item \scriptsize{Deployed advanced distribution patterns including sharding for log processing and
        refined caching strategies that reduced API calls to Rewards and third-party systems by 90\%.}

    \item \scriptsize{Led the migration of Bing's Content Discovery \& Selection critical offline pipelines from
        Cosmos Scope to Apache Spark, reducing operational costs by ~20\% across large-scale data platform
        services while enhancing performance, resulting in potential savings in the hundreds of millions of
        dollars.}
    
    \item \scriptsize{Enhanced data freshness for Food Recipes pipeline from 7 days to under 2 days by optimizing
        pipeline performance and transitioning from weekly to daily execution, making it the first project to
        adopt a new document ingestion platform.}
    
    \item \scriptsize{Reengineered PipelineManager configuration framework, resulting in 30\% performance increase
        across all Bing's Content Discovery \& Selection bucketed pipelines without requiring modification to job
        implementations.}

    \item \scriptsize{Designed BI dashboards that transformed raw data into visual analytics, enabling data-informed strategy 
        development and quantifiable business outcomes.}

    \item \scriptsize{Integrated Sponsored Stories in Microsoft Ads, generating ~\$2.5M in revenue for high-traffic
        integrations while ensuring seamless user experience.}

    \item \scriptsize{Leveraged Knowledge Cards template system with flexible schema design, expanding data
        scalability and enabling the addition of over 100 million entities while maintaining sub-100ms response
        times.}

    \item \scriptsize{Actively participated in neurodiversity and mental health initiatives that improved team
        collaboration and support for neurodivergent individuals by mentoring colleagues, advocating for inclusive
        workplace practices and being a founding member of the Mental Health \& Neurodiversity group within the
        local Disability ERG chapter in Brazil.}
\end{itemize}