% Software Engineer Cover Letter

\newcommand{\COMPANY}{DoorDash}
\newcommand{\POSITION}{Software Engineer, Backend (All Teams)}
\newcommand{\SOURCE}{DoorDash Careers Page}
\newcommand{\PRODUCT}{3-sided marketplace connecting Consumers, Merchants and Dashers}
\newcommand{\SPECIFICREASON}{your focus on building the world's most reliable on-demand logistics engine and transition from a monolithic architecture to a microservice-based one}
\newcommand{\RELEVANTTECHNOLOGY}{microservice architectures and distributed systems}
\newcommand{\TEAMNAME}{Backend Engineering team}

% ==== RECIPIENT INFORMATION ====
\noindent Hiring Team at \COMPANY
\vspace{0.4cm}

% ==== SALUTATION ====
\noindent Dear Hiring Team,
\vspace{0.4cm}

% ==== OPENING PARAGRAPH ====
I am writing to express my interest in the \POSITION{} position at \COMPANY, which I discovered through \SOURCE. With over nine years of experience building scalable backend services and high-performance APIs at Microsoft and Google, I am particularly drawn to \COMPANY's work on \PRODUCT{} and believe my technical background makes me well-suited for this role.

% ==== BODY PARAGRAPH 1 - TECHNICAL EXPERTISE ====
At Microsoft's AI Spartans team, I have specialized in accelerating high-priority projects by providing engineering expertise across diverse teams. I've designed and implemented microservice architectures for low-latency critical services, including Bing's Image Creator's UserHistoryV2 REST API, reducing API calls to other services by 90\% through refined caching strategies. At Google, I engineered fault-tolerant streaming pipelines processing 11 billion log entries daily. My experience with large-scale distributed systems, RESTful API design, and performance optimization directly aligns with developing large-scale web applications while improving performance, reliability, scalability, and security.

% ==== BODY PARAGRAPH 2 - SOFT SKILLS ====
Beyond technical skills, I excel in collaborative environments where cross-functional teamwork is essential. My role in Microsoft's Spartans team has honed my ability to quickly adapt to new technical environments, understand complex business requirements, and deliver impactful solutions within tight timeframes. I've successfully collaborated with teams across multiple organizations, ensuring seamless integration between disparate systems while establishing monitoring systems with alerting capabilities to maintain 99.9\% service availability—a skill that would transfer well to operating DoorDash's critical 24x7 global infrastructure.

% ==== BODY PARAGRAPH 3 - COMPANY-SPECIFIC INTEREST (OPTIONAL) ====
I am particularly interested in joining \COMPANY{} because \SPECIFICREASON. I believe my experience with \RELEVANTTECHNOLOGY{} would allow me to make meaningful contributions to your \TEAMNAME. I am excited about the opportunity to be involved in transitioning your monolithic codebase to a microservice-based architecture while tackling bleeding-edge technical problems that disrupt logistics and improve the experience for all users of your platform.

% ==== CLOSING PARAGRAPH ====
Thank you for considering my application. I look forward to the possibility of discussing how my background in backend engineering, distributed systems, and service architecture can contribute to DoorDash's continued growth and innovation in the logistics space.