% Software Engineer Cover Letter

\newcommand{\COMPANY}{DoorDash}
\newcommand{\POSITION}{Software Engineer, Build Platform}
\newcommand{\SOURCE}{DoorDash Careers Page}
\newcommand{\PRODUCT}{reliable, scalable build infrastructure}
\newcommand{\SPECIFICREASON}{your commitment to providing reliable, scalable, and repeatable cloud infrastructure that empowers thousands of developers to build and deploy great products quickly and safely}
\newcommand{\RELEVANTTECHNOLOGY}{performance optimization and pipeline automation}
\newcommand{\TEAMNAME}{Build \& Deploy Platform team}

% ==== RECIPIENT INFORMATION ====
\noindent Hiring Team at \COMPANY
\vspace{0.4cm}

% ==== SALUTATION ====
\noindent Dear Hiring Team,
\vspace{0.4cm}

% ==== OPENING PARAGRAPH ====
I am writing to express my interest in the \POSITION{} position at \COMPANY, which I discovered through \SOURCE. With over nine years of experience building scalable backend services and high-performance APIs at Microsoft and Google, I am particularly drawn to \COMPANY's work on \PRODUCT{} and believe my technical background makes me well-suited for this role.

% ==== BODY PARAGRAPH 1 - TECHNICAL EXPERTISE ====
At Microsoft's AI Spartans team, I have specialized in accelerating high-priority projects by providing engineering expertise across diverse teams. I've reengineered a pipeline management framework that resulted in a 30\% performance improvement across all Bing's Content Discovery and Selection bucketed pipelines without requiring modification to job implementations. At Google, I built comprehensive test automation and CI/CD pipelines to ensure high code quality, reliability, faster bug detection, and accelerated releases. These experiences directly align with optimizing build speeds, managing dependencies effectively, and enhancing caching strategies for your Bazel-based build system.

% ==== BODY PARAGRAPH 2 - SOFT SKILLS ====
Beyond technical skills, I excel in collaborative environments where cross-functional teamwork is essential. My role in Microsoft's Spartans team has honed my ability to quickly adapt to new technical environments, understand complex business requirements, and deliver impactful solutions within tight timeframes. I've consistently demonstrated the ability to analyze complex systems, identify performance bottlenecks, and implement scalable solutions that improve developer productivity—skills that would transfer well to implementing self-healing and auto-scaling solutions for DoorDash's build and test infrastructure.

% ==== BODY PARAGRAPH 3 - COMPANY-SPECIFIC INTEREST (OPTIONAL) ====
I am particularly interested in joining \COMPANY{} because \SPECIFICREASON. I believe my experience with \RELEVANTTECHNOLOGY{} would allow me to make meaningful contributions to your \TEAMNAME. I am excited about the opportunity to enhance developer experience across DoorDash by improving build performance, optimizing monorepo tooling, and scaling CI/CD infrastructure to support your growing organization.

% ==== CLOSING PARAGRAPH ====
Thank you for considering my application. I look forward to the possibility of discussing how my background in system optimization and pipeline engineering can contribute to DoorDash's build platform and help your developers ship high-quality code with confidence.