% Software Engineer Cover Letter

\newcommand{\COMPANY}{DoorDash}
\newcommand{\POSITION}{Software Engineer, Backend - Experimentation Platform}
\newcommand{\SOURCE}{DoorDash Careers Page}
\newcommand{\PRODUCT}{state-of-the-art Experimentation Platform}
\newcommand{\SPECIFICREASON}{your team's groundbreaking work on democratizing experimentation with quality and velocity, as highlighted in your publications about increasing logistics experiment capacity by 1000\% through parallelization and increased sensitivity}
\newcommand{\RELEVANTTECHNOLOGY}{large-scale data processing and statistical analysis systems}
\newcommand{\TEAMNAME}{Experimentation Analysis Platform team}

% ==== RECIPIENT INFORMATION ====
\noindent Hiring Team at \COMPANY
\vspace{0.4cm}

% ==== SALUTATION ====
\noindent Dear Hiring Team,
\vspace{0.4cm}

% ==== OPENING PARAGRAPH ====
I am writing to express my interest in the \POSITION{} position at \COMPANY, which I discovered through \SOURCE. With over nine years of experience building scalable backend services and high-performance APIs at Microsoft and Google, I am particularly drawn to \COMPANY's work on \PRODUCT{} and believe my technical background makes me well-suited for this role.

% ==== BODY PARAGRAPH 1 - TECHNICAL EXPERTISE ====
At Microsoft's AI Spartans team, I have specialized in accelerating high-priority projects by providing engineering expertise across diverse teams. I've enhanced data freshness for Food Recipes pipeline from 7 days to under 2 days by optimizing pipeline performance and transitioning to daily execution. At Google, I designed fault-tolerant streaming pipelines processing 11 billion log entries (100+ TiB) daily by implementing advanced sharding and replication patterns. My experience optimizing large-scale data pipelines has consistently delivered tangible business value through improved data freshness and processing efficiency, skills directly applicable to developing cutting-edge experimentation features supporting thousands of monthly experiments.

% ==== BODY PARAGRAPH 2 - SOFT SKILLS ====
Beyond technical skills, I excel in collaborative environments where cross-functional teamwork is essential. My role in Microsoft's Spartans team has honed my ability to quickly adapt to new technical environments, understand complex business requirements, and deliver impactful solutions within tight timeframes. At Google, I engineered cross-team survey infrastructure enabling teams across YouTube, Geo, Search, and Assistant to collect user feedback, much like how your Experimentation Platform team works with Product Engineers, Data Scientists, and ML Engineers to democratize experimentation with quality and velocity.

% ==== BODY PARAGRAPH 3 - COMPANY-SPECIFIC INTEREST (OPTIONAL) ====
I am particularly interested in joining \COMPANY{} because \SPECIFICREASON. I believe my experience with \RELEVANTTECHNOLOGY{} would allow me to make meaningful contributions to your \TEAMNAME. I am excited about the opportunity to help build platforms that can evolve to handle new statistical methodologies, machine learning technologies, and advanced causal inference techniques that drive business impact through experimentation.

% ==== CLOSING PARAGRAPH ====
Thank you for considering my application. I look forward to the possibility of discussing how my background in scalable data systems and performance optimization can contribute to advancing DoorDash's experimentation capabilities and supporting your mission of equipping decision makers with rigorous, data-driven insights.