%----------------------------------------------------------------------------------------
%   MICROSOFT
%----------------------------------------------------------------------------------------

\normalsize{Software Engineer 2 at \textbf{Microsoft}, Microsoft AI Spartans team}\\
        \scriptsize{São Paulo-SP, Brazil \& Redmond, WA, USA (Jun 2019 - Present)}
\begin{itemize}
    \item \footnotesize{Languages \& Technologies:}\scriptsize{ \textbf{C\#}, \textbf{Microsoft Cosmos Scope Script}, \textbf{Go}, \textbf{Scala}, \textbf{Java}, \textbf{.NET Spark}, \textbf{Azure}, HTML, CSS, PowerBI}
    \item \footnotesize{Key Responsibilities:}
    \begin{itemize}
        \item \scriptsize{As part of an elite engineering team, accelerated high-priority projects across Microsoft AI org by providing specialized engineering expertise to diverse teams, often joining projects at critical junctures to drive successful outcomes.}
        \item \scriptsize{Architected and maintained highly scalable backend services and RESTful APIs for high-traffic applications, implementing multi-tenant architecture patterns and secure API designs that supported millions of daily requests.}
        \item \scriptsize{Led mission-critical pipeline technology migrations (Microsoft Scope to Apache Spark/.NET Spark) optimizing performance for processing petabytes of data in enterprise-scale distributed systems while maintaining business continuity.}
        \item \scriptsize{Implemented robust error handling according to REST best practices, significantly improving API reliability through comprehensive exception management, rate limiting, and circuit-breaking patterns.}
        \item \scriptsize{Designed and implemented data exchange interfaces using JSON, XML, Protocol Buffers and Microsoft Bond to ensure seamless compatibility between Microsoft services and third-party platforms.}
        \item \scriptsize{Established comprehensive monitoring systems with real-time alerting capabilities to maintain 99.9\% service availability and ensure rapid response to production incidents.}
        \item \scriptsize{Engineered financial tracking and inventory management systems for Microsoft Rewards integration, implementing secure transaction processing with robust audit trails.}
        \item \scriptsize{Leveraged and enhanced CI/CD pipelines to streamline deployment processes, enabling faster release cycles and reducing production incidents through improved automation.}
        \item \scriptsize{Developed specialized testing tools including a Diff job tool for validating migrated pipeline outputs and implemented Nightwatch tests for API endpoints, improving system reliability.}
        \item \scriptsize{Collaborated with cross-functional teams to design system architecture that balanced performance, scalability, security, and cost efficiency according to enterprise standards.}
        \item \scriptsize{Advocated for neurodiversity and inclusion initiatives, actively mentoring and supporting colleagues to foster an inclusive workplace culture.}
    \end{itemize}
    \item \footnotesize{Key Achievements:}
    \begin{itemize}
        \item \scriptsize{\textsc{Data Pipelines \& Distributed Systems:}}
        \begin{itemize}
            \item \scriptsize{Migrated critical offline pipelines from Bing's content Discovery and Selection, reducing operational costs by ~20\% while improving performance, with potential savings in the hundreds of millions across the organization.}
            \item \scriptsize{Enhanced data freshness for Food Recipes pipeline from 3–7 days to under 1–2 days by transitioning from weekly to daily pipeline execution and integrating a new internal technology, improving real-time data relevance and making it the first project to adopt the new system for ingesting web documents parsed content.}
            \item \scriptsize{Architected multilingual Query Parser pipelines supporting 40+ languages and markets, implementing sophisticated parallel processing techniques that maintained high accuracy while enabling seamless multilingual integration.}
            \item \scriptsize{Applied advanced performance optimization techniques to critical data pipelines, reducing execution time from 10-20 hours to approximately 5 hours through improved parallelization strategies and resource allocation.}
            \item \scriptsize{Reengineered PipelineManager configuration framework, resulting in 30\% performance increase across all bucketed pipelines in the Discovery org without requiring modification to job implementations.}
            \item \scriptsize{Designed and implemented innovative catchup solution for historical data processing, reducing estimated catchup time from 6 months to 1 week for a business-critical data pipeline through intelligent data partitioning and incremental processing.}
            \item \scriptsize{Successfully managed complex pipeline migrations with zero downtime, maintaining system stability during transitions through comprehensive planning, testing, and rollback strategies.}
        \end{itemize}

        \item \scriptsize{\textsc{Web Services \& APIs:}}
        \begin{itemize}
            \item \scriptsize{Designed and implemented microservice architectures for critical systems including the \textbf{ImageGenerator UserHistory API} and MMSBI logging system, focusing on scalability, maintainability, and service isolation to support user token management and integration with external systems.}
            \item \scriptsize{Applied advanced distribution patterns including sharding when processing logs and implemented sophisticated caching strategies that reduced the number of API calls to Rewards and third-party systems by 90\% while significantly reducing latency for high-volume operations.}
            \item \scriptsize{Architected Knowledge Cards template system using a flexible schema design, increasing data scalability and enabling the addition of over 100 million entities while maintaining sub-100ms response times.}
            \item \scriptsize{Led integration with multiple external payment and authentication systems (e.g., PayPal, Rewards), implementing secure token exchange protocols to ensure reliable and secure data transactions between disparate platforms.}
            \item \scriptsize{Developed a generic Refund API and comprehensive Points Inventory Management System for Microsoft Rewards with a future-proof architecture designed to accommodate evolving business requirements beyond initial specifications.}
            \item \scriptsize{Engineered sophisticated goroutine parallelization with custom pooling and queueing systems for retry caching in the Microsoft Ads logging infrastructure, significantly improving throughput while maintaining data consistency.}
            \item \scriptsize{Leveraged replication patterns in Microsoft Cosmos and HDFS to ensure data durability and processing efficiency across distributed systems.}
            \item \scriptsize{Enhanced auto-replenish feature for ImageGenerator tokens through sophisticated business logic that balanced conflicting requirements from multiple stakeholders while maintaining a seamless user experience.}
        \end{itemize}
        
        \item \scriptsize{\textsc{Tools \& Automation:}}
        \begin{itemize}
            \item \scriptsize{Developed tools and libraries, which streamlined migration validation, ensuring accurate and efficient workflows.}
            \item \scriptsize{Leveraged CI/CD pipelines to streamline deployment processes, enabling faster release cycles and reducing production incidents.}
            \item \scriptsize{Enhanced internal tools with new safety measures, logging, and configuration options, boosting reliability and scalability.}
            \item \scriptsize{Designed and delivered comprehensive analytics dashboards integrating visualization technologies.}
            \item \scriptsize{Created testing tools including a Diff job tool for validating migrated pipeline outputs and Nightwatch tests for API endpoints.}
            \item \scriptsize{Updated security on internal spark modules to passwordless AAD Token authentication, enhancing system security while maintaining ease of use.}
            \item \scriptsize{Became second top committer to core WebDataPlatform team's PipelineManager through numerous improvements and features.}
            \item \scriptsize{Improved repository infrastructure through Corext aliases enhancements, boosting development efficiency.}
        \end{itemize}

        \item \scriptsize{\textsc{Cross-Team Contributions \& Impact:}}
        \begin{itemize}
            \item \scriptsize{Implemented logging infrastructure improvements for Microsoft Ads, preventing data loss and increasing reliability for BI decisions.}
            \item \scriptsize{Integrated Sponsored Stories in Microsoft Ads, generating ~\$2.5M in revenue for high-traffic integrations.}
            \item \scriptsize{Supported UX enhancements for Knowledge Cards, improving accessibility and creating visually appealing templates for diverse content types.}
            \item \scriptsize{Successfully enabled product deployment in international markets, expanding global reach for services including Trending Topics for Microsoft Ads and Bing Search's QueryParser.}
            \item \scriptsize{Identified and resolved critical bugs affecting end users, including a long-standing high-priority issue related to non-trending content in trending scenarios.}
            \item \scriptsize{Facilitated comprehensive knowledge transfer and onboarding sessions for team members on both internal tools like Cosmos and public tools like .NET Spark.}
            \item \scriptsize{Successfully completed handoff of complex systems with detailed documentation, ensuring seamless transitions.}
        \end{itemize}

        \item \scriptsize{\textsc{Troubleshooting \& Reliability:}}
        \begin{itemize}
            \item \scriptsize{Led incident response teams diagnosing and resolving complex production issues under high-pressure situations across distributed systems.}
            \item \scriptsize{Built automated recovery systems that could detect, diagnose, and remediate service failures with minimal interruption.}
            \item \scriptsize{Created systematic approaches to identify potential system vulnerabilities through proactive monitoring and analysis.}
            \item \scriptsize{Implemented comprehensive monitoring and alerting systems that significantly reduced mean time to detection for production incidents, improving overall system reliability.}
        \end{itemize}

        \item \scriptsize{\textsc{System Resiliency \& Optimization:}}
        \begin{itemize}
            \item \scriptsize{Led incident response teams diagnosing and resolving complex production issues under high-pressure situations across distributed systems.}
            \item \scriptsize{Built automated recovery systems that could detect, diagnose, and remediate service failures with minimal interruption.}
            \item \scriptsize{Applied advanced distribution patterns including sharding when processing logs and implemented sophisticated caching strategies that reduced API calls by 90\% while significantly reducing latency.}
            \item \scriptsize{Engineered sophisticated goroutine parallelization with custom pooling and queueing systems, significantly improving throughput while maintaining data consistency.}
            \item \scriptsize{Leveraged replication patterns in Microsoft Cosmos and HDFS to ensure data durability and processing efficiency across distributed systems.}
        \end{itemize}

        \item \scriptsize{\textsc{Diversity \& Inclusion:}}
        \begin{itemize}
            \item \scriptsize{Actively participated in NeuroDiversity ERG, fostering ADHD awareness and mentoring colleagues to create an inclusive, supportive environment.}
            \item \scriptsize{Advocated for DEI initiatives through events and projects, promoting mental health awareness and accessibility.}
        \end{itemize}
    \end{itemize}
\end{itemize}
