%----------------------------------------------------------------------------------------
%   Google
%----------------------------------------------------------------------------------------

\normalsize{Backend Software Engineer at \textbf{Google}, Google Proactive Team (Search Growth)}\\
        \scriptsize{Belo Horizonte-MG, Brazil (Jan 2016-Jun 2019)}
\begin{itemize}
    \item \footnotesize{Technologies:}\scriptsize{ \textbf{C++}, \textbf{Java}, \textbf{Python}, \textbf{GCP}, \textbf{BigQuery}, \textbf{Bigtable}, \textbf{Cloud Dataflow}, Protocol Buffers, gRPC, Pub/Sub}
    \item \footnotesize{Key Responsibilities:}
    \begin{itemize}
        \item \scriptsize{Architected and implemented high-performance distributed backend systems following agile development principles, focusing on scalability, reliability, and maintainability for high-volume data processing applications.}
        \item \scriptsize{Designed and developed streaming services and RESTful APIs for near real-time data processing through the \emph{Google Opinion Rewards} app and Search Web Results, implementing sophisticated data transformation and analysis pipelines that informed growth initiatives.}
        \item \scriptsize{Collaborated with cross-functional teams to define service interfaces and integration points, ensuring seamless communication between system components while balancing competing technical requirements.}
        \item \scriptsize{Implemented comprehensive test automation and CI/CD pipelines to ensure high code quality and reliability in production environments.}
    \end{itemize}
    \item \footnotesize{Key Achievements:}
    \begin{itemize}
        \item \scriptsize{Designed and deployed a fault-tolerant streaming pipeline capable of processing 11 billion log entries per day (100TiB+) with high availability, implementing advanced data sharding and replication patterns to ensure system reliability.}
        \item \scriptsize{Provided comprehensive adoption support across YouTube, Geo, Search, and Assistant teams, facilitating seamless integration and helping stakeholders implement our systems, indirectly impacting millions of users.}
        \item \scriptsize{Contributed to cross-team survey infrastructure used by multiple Google organizations to collect user feedback, enabling product improvements across the company.}
        \item \scriptsize{Worked with distributed storage solutions to handle large data volumes with proper consistency controls and implemented sophisticated error handling mechanisms for greater fault tolerance.}
    \end{itemize}
\end{itemize}
