%----------------------------------------------------------------------------------------
%   INTERNSHIPS
%----------------------------------------------------------------------------------------

\normalsize{Full Stack Software engineer intern at \textbf{TAPPS Games}, Mobile Casual Games Development Team}\\
        \scriptsize{São Paulo-SP, Brazil (May 2015-Sep 2015)}
\begin{itemize}
    \item \footnotesize{Languages:}\scriptsize{ \textbf{Lua}}
    \item \footnotesize{Key Responsibilities:}\scriptsize{ Developed both new games and re-skins of old games as a back-end and front-end developer for high-performance gaming applications.}
    \item \footnotesize{Key Achievements:}\scriptsize{ Contributed to the successful launch of 5 mobile games achieving over 30M downloads with average rating of 4.6+. Developed both backend and frontend components for gaming applications. Acted in the \href{https://www.youtube.com/watch?v=ttjWkk9w-8Q}{teaser video} of one of the games.}
\end{itemize}

%------------------------------------------------

\normalsize{Back-end Software engineer intern at \textbf{Google}, Social Infrastructure team}\\
        \scriptsize{Belo Horizonte-MG, Brazil (Dec 2014-Feb 2015)}
\begin{itemize}
    \item \footnotesize{Languages:}\scriptsize{ \textbf{Go}}
    \item \footnotesize{Key Responsibilities:}\scriptsize{ Contributed to a system to analyze server profiles and detect differences using hypothesis testing. It assessed whether \textit{Social} org systems updates, like Google+, outperformed previous versions and used veto power to prevent poorly performing updates from being released.}
    \item \footnotesize{Key Achievements:}\scriptsize{ Shipped to production and, at the time, became a standard in the Social org to run those tests. Improved the precision of statistical analysis by 10\% through enhancements to the hypothesis testing methodology.}
\end{itemize}

%------------------------------------------------

\normalsize{Full Stack Software developer intern at \textbf{Drivedata Software}}\\
        \scriptsize{São Paulo-SP, Brazil (Oct 2013-Oct 2014)}
\begin{itemize}
    \item \footnotesize{Languages:}\scriptsize{ \textbf{Java}, HTML, CSS}
    \item \footnotesize{Key Responsibilities:}\scriptsize{ Designed and developed a Java Web application and an Android App related to vehicle insurance companies.}
    \item \footnotesize{Key Achievements:}\scriptsize{ Developed the signed in user interface web application and the android application that were shipped for the first launch of the company. Delivered production-ready code that was essential to the company's market entry.}
\end{itemize}

%------------------------------------------------

\normalsize{Full Stack Software developer intern at \textbf{CCSL}, Mezuro \& Kalibro Team}\\
        \scriptsize{São Paulo-SP, Brazil (Sep 2010-Jan 2013)}
\begin{itemize}
    \item \footnotesize{Languages:}\scriptsize{ \textbf{Java}, \textbf{Ruby}, HTML, CSS, JavaScript}
    \item \footnotesize{Key Responsibilities:}\scriptsize{ Collaborated on the development of the Kalibro and Mezuro projects at CCSL (\href{http://ccsl.ime.usp.br/en}{ccsl.ime.usp.br/en}). Contributed to research on code metrics in Free/Libre and Open Source Software (FLOSS).}
    \item \footnotesize{Key Achievements:}\scriptsize{ Co-Presented and contributed to a Poster and a presentation with research and development results in international conferences, enhancing the academic community's understanding of code metrics. Contributed to the development of the Kalibro and Mezuro projects at CCSL, focusing on the advancement of tools for code metrics analysis.}
    \item \footnotesize{Note about this experience:}\scriptsize{ Since it was close to an academic environment we could follow XP programming and other agile practices by the book, such as TDD, Planning Game, on-site customer, Daily stand-ups, Kanban, Pair Programming and Continuous integration.}
\end{itemize}

%---------- ALTERNATE VERSION -------------

%\subsection{Early Career Experience}
%\begin{itemize}
%    \item \footnotesize{Back-end Software engineer intern at \textbf{Google}, Social Infrastructure team (Dec 2014-Feb 2015)}
%    \begin{itemize}
%        \item \scriptsize{Contributed to a system analyzing server profiles to detect performance differences using hypothesis testing, which became a standard validation tool for the Social org's production releases.}
%        \item \scriptsize{Improved the precision of statistical analysis by 10\% through enhancements to the hypothesis testing methodology.}
%    \end{itemize}
%
%    \item \footnotesize{Previous Internships (2010-2015)}
%    \begin{itemize}
%        \item \scriptsize{Gained foundational experience in software development at TAPPS Games, Drivedata Software, and CCSL, working with Java, Ruby, and Lua across web, mobile, and research applications.}
%        \item \scriptsize{Practiced agile methodologies including TDD, Pair Programming, and Continuous Integration in academic and professional environments.}
%    \end{itemize}
%\end{itemize}