%----------------------------------------------------------------------------------------
%	EDUCATION
%----------------------------------------------------------------------------------------

\section{Education}

\begin{itemize}
    \item \footnotesize{Bachelor Degree in \textsc{Computer Science} at the \textbf{University of São Paulo}, São Paulo-SP, Brazil}\\
    \textsc{\scriptsize{Feb 2011-Dec 2015}}
    \begin{itemize}
        \item \scriptsize{Relevant coursework: Distributed Systems, Algorithm Analysis, Database Design, Software Engineering, Operating Systems, Linear Programming, Programming Languages.}
    \end{itemize}

    \item \footnotesize{Exchange Semester at the \textbf{Università della Svizzera Italiana}, Lugano-TI, Switzerland}\\
    \textsc{\scriptsize{Feb 2013-Jun 2013}}
    \begin{itemize}
        \item \scriptsize{Focus on Advanced Software Architecture and research in Code Quality and Code Metrics Analysis.}
    \end{itemize}
\end{itemize}

\section{Other Courses}

\begin{itemize}
    \item \footnotesize{\textbf{Microsoft Professional Development (2025):}}\scriptsize{ Responsible AI (4-hour) and Copilot/Prompt Engineering (8-hour) training paths.}
    
    \item \footnotesize{\textbf{K19 Trainings}, São Paulo-SP, Brazil,}\scriptsize{ 2011}
    \begin{itemize}
        \item \scriptsize{\textsc{Web Development with JSF2 and JPA} training.}
        \item \scriptsize{\textsc{Persistence with JPA2 and Hibernate} training.}
        \item \scriptsize{\textsc{Advanced Web Development with JSF2, EJB3.1 and CDI} training.}
        \item \scriptsize{\textsc{System Integration with Web services, JMS and EJB} training.}
    \end{itemize}

    \item \footnotesize{\textbf{Caelum Trainings}, São Paulo-SP, Brazil,}\scriptsize{ 2009}
    \begin{itemize}
        \item \scriptsize{\textsc{Java and OO} training.}
        \item \scriptsize{\textsc{Java Laboratory with Tests, XML and Design Patterns} training.}
        \item \scriptsize{\textsc{Java for WEB Development} training.}
    \end{itemize}

    \item \footnotesize{\textbf{CPORAer}, São José dos Campos-SP, Brazil,}\scriptsize{ 2007-2009}\\
        \scriptsize{Preparatory course for airforce's reserve officers}.
\end{itemize}

\section{Professional Development}
\begin{itemize}
    \item \footnotesize{\textbf{Microsoft Professional Development (2025):}}\scriptsize{ Responsible AI (4-hour) and Copilot/Prompt Engineering (8-hour) training paths.}
    \item \footnotesize{\textbf{LinkedIn Learning (2021):}}\scriptsize{ "Enhancing Resilience" certificate program focused on developing resilience strategies for peak performance in challenging environments.}
    \item \footnotesize{\textbf{Diversity, Equity \& Inclusion:}}\scriptsize{ Attended International Conference on ADHD (2020-2022), focusing on neurodiversity, workplace inclusion, productivity and mental health awareness.}
\end{itemize}