%----------------------------------------------------------------------------------------
%   MICROSOFT
%----------------------------------------------------------------------------------------

\normalsize{Software Engineer 2 at \textbf{Microsoft}, Microsoft AI Spartans team}\\
        \scriptsize{São Paulo-SP, Brazil \& Redmond, WA, USA (Jun 2019 - Mar 2025)}
\begin{itemize}
    \item \scriptsize{As part of Spartans, an \textbf{elite engineering team}, accelerated high-priority projects across Microsoft AI org by providing \textbf{specialized engineering expertise}, joining projects at critical junctures to drive successful outcomes.}
    
    \item \scriptsize{Migrated \textbf{critical offline pipelines} from Bing's content Discovery and Selection, reducing operational costs by \textbf{~20\%} while improving performance, with potential savings in the hundreds of millions.}
    
    \item \scriptsize{Enhanced data freshness for Food Recipes pipeline from 3–7 days to under 1–2 days by transitioning from weekly to daily execution, making it the first project to adopt a new document ingestion platform.}
    
    \item \scriptsize{Reengineered \textbf{PipelineManager} configuration framework, resulting in \textbf{30\%} performance increase across all Bing's Discovery \& Selection bucketed pipelines without requiring modification to job implementations.}
    
    \item \scriptsize{Implemented \textbf{advanced distribution patterns} including sharding for log processing and sophisticated caching strategies that reduced API calls to Rewards and third-party systems by \textbf{90\%}.}
    
    \item \scriptsize{Engineered \textbf{sophisticated goroutine parallelization} with custom pooling and queueing systems for retry caching in Microsoft Ads logging infrastructure, significantly improving throughput while maintaining data consistency.}
    
    \item \scriptsize{Designed and implemented \textbf{microservice architectures} for critical systems including the ImageGenerator UserHistory API, focusing on scalability, maintainability, and service isolation.}
    
    \item \scriptsize{Established \textbf{monitoring systems} with alerting capabilities to maintain \textbf{99.9\%} service availability with rapid incident response.}

    \item \scriptsize{Developed \textbf{monitoring systems} that provided actionable insights for driving business decisions.}

    \item \scriptsize{Integrated Sponsored Stories in Microsoft Ads, generating \textbf{~\$2.5M} in revenue for high-traffic integrations while ensuring seamless user experience.}

    \item \scriptsize{Leveraged \textbf{Knowledge Cards} template system using flexible schema design, increasing data scalability and enabling the addition of over 100 million entities while maintaining sub-100ms response times.}

    \item \scriptsize{Engineered \textbf{financial tracking and inventory management} systems for Microsoft Rewards integration, implementing secure transaction processing with robust audit trails.}

    \item \scriptsize{Actively participated in neurodiversity initiatives, mentoring colleagues and advocating for inclusive workplace practices that improved team collaboration.}
    
    \item \scriptsize{Founded the \textbf{Mental Health \& Neurodiversity initiative} within the local Disability ERG chapter in Brazil, advocating for inclusive workplace practices and supporting neurodivergent colleagues.}
\end{itemize}