%----------------------------------------------------------------------------------------
%	SKILLS & COMPETENCIES
%----------------------------------------------------------------------------------------

\section{Skills}


\begin{itemize}
    \item \small{\titlecap{Cloud and Distributed Systems:}}\footnotesize{ \titlecap{Azure, GCP,
        Cloud-Native Services, Microservices Architecture, REST API Design Patterns, Caching Strategies,
        Low-Latency Services, High-Availability, Fault Tolerance, Container Orchestration (Kubernetes
        and Docker), Message Brokers (Apache Kafka, Azure Service Bus), Multi-tenant Systems, 
        Consensus algorithms, CAP theorem, Eventual Consistency, High-Performance Computing (HPC).}}

    \item \small{\titlecap{Data Engineering:}}\footnotesize{ \titlecap{Large Datasets Processing,
        Data Pipelines Design and Development, Apache Spark, Apache Beam, ETL, High-Performance Data 
        Delivery, Data Governance, Real-time Analytics, Streaming Data, Data Modeling,
        Distributed Transaction Models, Dataflow, BI Dashboards.}}
       
    \item \small{\titlecap{Data Storage:}}\footnotesize{ \titlecap{Distributed Storage Solutions 
        (HDFS, Parquet, ORC), Cloud Storage (Google Cloud Storage, Azure Data Lake, Filestore, BigQuery, 
        Pub/Sub), NoSQL Databases (BigTable, Azure Key-Value Data Store), SQL Databases, Tiered Storage
        Management.}}

    \item \small{\titlecap{Programming Languages and Frameworks:}}\footnotesize{ \titlecap{\LanguagesOrderSkills}.}
    
    \item \small{\titlecap{AI/ML:}}\footnotesize{ \titlecap{AI/ML Fundamentals, Prompt Engineering, 
        Data Ingestion and Preparation.}}
        
    \item \small{\titlecap{CS Fundamentals and Software Engineering:}}\footnotesize{ \titlecap{
        MSBuild, Blaze, CI/CD, Software Design, Backend Architecture, A/B Testing, Test Automation and
        Test-Driven Development, Agile (XP and Scrum), Code Quality Analysis, Concurrency and
        Parallelism, Algorithms and Data Structures, Performance Optimization, DevOps, SDLC.}}
    
    \item \small{\titlecap{Observability and Reliability:}}\footnotesize{ \titlecap{Metrics 
        Collection and Analysis, Logging Infrastructure, Distributed Tracing, Alerting Systems, Incident 
        Response, Service Health Monitoring, Performance Profiling, SLO/SLI Management, Root Cause 
        Analysis (Fault Tree Analysis, 5 Whys), Postmortem Processes.}}

    \item \small{\titlecap{Professional Skills:}}\footnotesize{ \titlecap{Cross-team Collaboration 
        and Interdisciplinary Work, Leadership, Collaborative Problem-Solving, Technical Adaptability, 
        High Aptitude to Learn, Stakeholder Communication, Technical Documentation, Requirements 
        Gathering, Growth Mindset, Distributed Teams Coordination, Constructive Feedback, Relationship 
        Building across Organizational Levels, Mentorship and Coaching.}}

    \item \small{\titlecap{Languages:}}\footnotesize{ \titlecap{English (Fluent), Portuguese 
        (Native).}}
\end{itemize}


